Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-09-09 date/paper.tex
Refined template

\begin{figure*}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
package com.sb.game;

import java.util.List;

public class GameScene
{
|\highlightYellow|	public void addToList(List l) {
|\highlightYellow|		l.add(getClass().getName());
|\highlightYellow|	}

	public void addTen(int x) {
|\highlightYellow|		x = x + 10; // Addition
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
package com.sb.fruitgame;

import java.awt.List; // Different type

public class LoseScene
{
|\highlightYellow|	public void addToList(List l) {
|\highlightYellow|		l.add(getClass().getName());
|\highlightYellow|	}

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concat
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Example of textually equal code fragments that differ in functionality.}
\label{fig:type1}
\end{figure*}

@@

\begin{figure*}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doB(a);
}
\end{javacode}}
\end{parcolumns}
\caption{A clone that spans a block partially.}
\label{fig:refactorabilitypartialblock}
\end{figure*}

@@

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

@@

@@

\bibliography{references}
